---
title: "DSc Assignment 1"
output:
  pdf_document: default
  html_notebook: default
---
By-
Shaurya Goel
(2016194)
```{r} 
# Import necessary packages
library(corrplot)
```

Load all the saved csv files (with provided links)
```{r} 
# https://cdiac.ess-dive.lbl.gov/trends/emis/tre_coun.html
co2=read.csv('CO2_emission.csv')

# https://data.gov.in/resources/monthly-seasonal-and-annual-mean-temp-series-1901-2017
temp=read.csv('Mean_Temp_IMD_2017.csv')

# https://data.gov.in/resources/frequency-cyclonic-disturbances-depressions-and-above-over-bay-bengal-bob-arabian-sea-and
cyclone=read.csv('cyclonic-disturbances-1891-2016.csv')

# https://data.gov.in/resources/district-rainfall-normal-mm-monthly-seasonal-and-annual-data-period-1951-2000
rainfall=read.csv('rainfall in india 1901-2015_stateswise.csv')

# https://data.worldbank.org/topic/climate-change
data=read.csv('WorldBank_data.csv')       # contains many variables
```

Getting desired data from the CO2 emission file
```{r}
co2=co2[co2$Nation=='INDIA',]
names(co2)[3] <- "Total.Emission"      # rename column name
co2=co2[,2:3]
rownames(co2)<-NULL                    # rename row name
```

Getting desired data from the temperature file
```{r}
temp=subset(temp,select=c('YEAR','ANNUAL'))
```

Getting desired data from the cyclone file
```{r}
cyclone=subset(cyclone,select=c('Year',"January...December..Whole.Year...Total" ))
names(cyclone)[2] <- "Total.Cyclones"   # rename column name
```

Getting desired data from the rainfall file
```{r}
rainfall=subset(rainfall,select=c('SUBDIVISION','YEAR','ANNUAL'))
rainfall[is.na(rainfall)]<-0
rainfall=aggregate(rainfall$ANNUAL,by=list(Category=rainfall$YEAR),FUN=mean)
names(rainfall[2]) <- "Total.Rainfall"
```

Getting desired data from the World Bank file
```{r}
data=data[c(4,61,68),]
data=t(data)
colnames(data) <- c("Total.Pop",'Electricity From Coal %','Forest.Area') # rename columns
data=data[c(-1,-2),]
rownames(data)<-1960:2018    # row names are from 1960-2018
data[is.na(data)]<-0         # Fill missing values with 0
class(data)<-"numeric"       # Convert all columns to numeric type
```

# ANALYSIS
```{r}
plot(co2[,1],co2[,2],xlab='Year',ylab='Total emission (in million Tonnes)', main='CO2 emission in India')
```

We can clearly see above that the total CO2 emission is increasing with each year.

```{r}
plot(rainfall[,1],rainfall[,2],xlab='Year',ylab='Total rainfall(in mm)',main='Average rainfall in India')
```
We can see that average rainfall is decreasing after 1940, possibly due to changing climatic patterns.

```{r}
plot(cyclone[,1],cyclone[,2],xlab='Year',ylab='Total cyclones', main='Total number of cyclones in India')
```
Similar to average rainfall, total cyclones are decreasing after 1940. Will this show high correlation?

```{r}
years=1960:2018
plot(years,data[,1],xlab='Year',ylab='Total Population', main='Total population of India')
```
Total population is increasing with each year.

```{r}
year=1971:2015
plot(year,data[year-1959,2],xlab='Year',ylab='% of total electricity generated', main='Coal used to generate electricity')
```
Usage of coal is on the rise since 1970.


# ANS-3
```{r}
plot(rainfall[1:nrow(rainfall),2],cyclone[11:125,2],xlab='rainfall (in mm)',ylab='number of cyclones',main='Cyclones vs Rainfall')
```
There is a slight upward trend indicating cyclones increase with amount of rainfall. If we took rainfall occuring in coastal regions only, then there would be a higher correlation.

```{r}
plot(co2[92:146,2],data[1:55,1],xlab='CO2 emission (in mil. tonnes)',ylab='Total population',main='Population vs CO2')
```
With increasing population more CO2 is emitted as people use fossil fuels.

```{r}
plot(co2[103:146,2],data[12:55,2],xlab='C02 generated',ylab='% electricity generated from coal',main='Electricity from coal vs CO2')
```
More electricity generated from coal means more CO2 in atmosphere. 

```{r}
plot(data[12:55,1],data[12:55,2],xlab='Population',ylab='% electricity generated from coal',main='Electricity vs population')
```
Higher population demands higher electricity. Also, it is easiest to generate electricity from coal, hence the upward trend.

```{r}
new_data=data.frame(co2[103:146,2],data[12:55,1],data[12:55,2])
colnames(new_data)<-c('CO2','Population','Coal')
corrplot(cor(new_data))
```
All three variables are highly correlated with each other which is expected. High population leads to high coal usage to generate electricity. Which leads to more emission of CO2.
